### 2014-10-14 ApTranscriptome_TR.Rmd
visualization of induction vs constitutive expression

**July 17, 2014**

@@

# merge results
Ap.response.type <- rbind(interaction.response.type, temperature.response.type)
colnames(Ap.response.type)[which(colnames(Ap.response.type) == ".id")] <- "Transcript"
str(Ap.response.type)

@@

mh_plot <- qplot(x=Apic, y=Acar, data=md, fill=value, geom="tile", ylim = rev(levels(md$Acar))) + 
  scale_fill_gradient2(limits=c(-600, 600)) 
mh_plot
```

@@

```{r induction_vs_constitutive}
Ap.constitutive <- resp.TPM.dt.sub.pred[resp.TPM.dt.sub.pred$val == ]

>>>>

**October 14, 2014**

@@

# merge results
Ap.response.type <- rbind(interaction.response.type, temperature.response.type)
colnames(Ap.response.type)[which(colnames(Ap.response.type) == ".id")] <- "Transcript"
Ap.response.type <- data.table(Ap.response.type)
setkey(Ap.response.type, Transcript)
str(Ap.response.type)

@@

mh_plot <- qplot(x=Apic, y=Acar, data=md, fill=value, geom="tile", ylim = rev(levels(md$Acar))) + 
  scale_fill_gradient2(limits=c(-600, 600)) +
  theme(axis.title = element_text(face="italic")) +
  labs(x = "A. picea", y = "A. carolinensis")

tiff("results/matched_observations_Fig1.tiff", compression = "lzw")
mh_plot
dev.off()
```

@@

```{r induction_vs_constitutive}
# calculate degree of induction
Ap.induction <- ddply(resp.TPM.dt.sub.pred, .(colony, Transcript), summarise, 
                      upreg = (max(pTPM) - min(pTPM))/min(pTPM) * 100 )
# merge optimum expression, in Ap.response.type data.frame, with predicted TPM data
Ap.induction <- data.table(Ap.induction)
setkey(Ap.induction, Transcript)
Ap.response.type2 <- Ap.induction[Ap.response.type]

# plot constitutive expression vs induction for High, Low and Bimodal genes only

setkey(Ap.response.type2, A22.type)
Ap.response.type2.up <- Ap.response.type2[A22.type!="Intermediate", ]
setkey(Ap.response.type2.up, Ar.type)
Ap.response.type2.up <- Ap.response.type2.up[Ar.type!="Intermediate", ]

gg5 <- ggplot(Ap.response.type2.up, aes(x = log(A22.opt), y = log(upreg), colour = A22.type)) + 
  geom_point() + 
  facet_grid(. ~ colony)

print(gg5)
```
